### 2013-12-18 Paper_Markdown.Rmd
Local changes to plotting.

**Abstract**
*Fossil pollen provides a widespread proxy for past vegetation.  It is increasingly used in paleoclimatic reconstruction, but the limits of its utility are not well known.  Methodological advances, such as the development of tests for spatial autocorrelation, and newer methods for climate reconstruction using boosted regression trees may improve the abilities of these climate reconstruction techniques, but little is known about the accuracy of these models under conditions of non-analogue vegetation known to occur at the end of the late glacial.  In this paper we generate non-analogue pollen assemblages by excluding close neighbours from calibration datasets at increasingly larger squared chord distances.  Using three standard and two newer techniques we then test the ability of pollen-based climate models to accurately recostruct climate under conditions of no-analogue vegetation.*

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, scales='free_y', nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(bias), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, scales='free_y', nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bias (RMSEP)')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(variance), group = site, color = init)) +
  geom_path(alpha = 0.05) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bootstrap Variance')

>>>>

**Abstract**
Fossil pollen provides a widespread proxy for past vegetation.  It is increasingly used in paleoclimatic reconstruction, but the limits of its utility are not well known.  Methodological advances, such as the development of tests for spatial autocorrelation, and newer methods for climate reconstruction using boosted regression trees may improve the abilities of these climate reconstruction techniques, but little is known about the accuracy of these models under conditions of non-analogue vegetation known to occur at the end of the late glacial.  In this paper we generate non-analogue pollen assemblages by excluding close neighbours from calibration datasets at increasingly larger squared chord distances.  Using three standard and two newer techniques we then test the ability of pollen-based climate models to accurately recostruct climate under conditions of no-analogue vegetation.

@@

ggplot(model.samp, aes(x = dissim, y = preds, group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0), limits=c()) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Predicted Value')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(bias), group = site, color = init)) +
  geom_path(alpha = 0.1) +
  theme_bw() +
  facet_wrap(~model, nrow = 1) +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bias (RMSEP)')

@@

ggplot(model.samp, aes(x = dissim, y = sqrt(variance), group = site, color = init)) +
  geom_path(alpha = 0.05) +
  theme_bw() +
  facet_wrap(~model, nrow = 1, scales='free_y') +
  scale_x_continuous(expand=c(0,0)) +
  scale_color_continuous(low='#F08080', high='#4169E1') +
  theme(legend.position = 'top',
        axis.title = element_text(family = 'serif', face = 'bold', size = 14),
        strip.text = element_text(family = 'serif', face = 'bold', size = 14),
        axis.text = element_text(family = 'serif', size = 10),
        strip.text = element_text(family = 'serif', face = 'bold', size = 12)) +
  xlab('Calibration Dissimilarity') +
  ylab('Bootstrap Variance')
